sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-24 doc/paper.Rmd
dir.create

```{r diagram, fig.cap="(ref:diagram-fig)"}
f <- here::here("figs", "diagram.pdf")
if (!file.exists(f)) {
  download.file("https://www.dropbox.com/s/j8km3hv8xz9b63k/diagram.pdf?dl=1", 
    destfile = f)
}
knitr::include_graphics(f)
```

>>>>

```{r diagram, fig.cap="(ref:diagram-fig)"}
dir.create("figs", showWarnings = FALSE)
f <- here::here("figs", "diagram.pdf")
if (!file.exists(f)) {
  download.file("https://www.dropbox.com/s/j8km3hv8xz9b63k/diagram.pdf?dl=1", 
    destfile = f)
}
knitr::include_graphics(f)
```
